### 2013-09-08 datasets/paper.tex
removed dataset blabla, maybe in appendix. added contained papers to the intro.

\chapter{Datasets and Evaluation Methodology}
This work uses several public datasets for semantic segmentation
and object class segmentation. This chapter briefly introduces each of the datasets,
and discusses its characteristic. The datasets we use are among the most well-known
and most-used datasets in the current semantic segmentation and object class segmentation
literature.

@@

Most of the classes in the MSRC-21 dataset can be well distinguished using local texture.
This is particularly true for the stuff classes, but also for the animal classes, buildings, and signs.
Consequently, many approaches use low-level approaches such as texton-boost or random forests as base features,
as these are particularly well-suited for the dataset.

\section{Pascal VOC}

\section{New York University RGB-D Segementation

>>>>

\chapter{Computer Vision Tools, Datasets and Evaluation}
This work uses several public datasets for semantic segmentation
and object class segmentation. This chapter briefly introduces each of the datasets,
and discusses its characteristic. The datasets we use are among the most well-known
and most-used datasets in the current semantic segmentation and object class segmentation
literature.

\section{Computer Vision Tools}
Textonboost
SIFT, SLIC, CPMC, BOW

@@

% Typical methods
Most of the classes in the MSRC-21 dataset can be well distinguished using local texture.
This is particularly true for the stuff classes, but also for the animal classes, buildings, and signs.
Consequently, many approaches use low-level approaches such as texton-boost or random forests as base features,
as these are particularly well-suited for the dataset.
%
Following this line of work, we use the texton-boost implementation provided by \citet{krahenbuhl2012efficient}
as a basis of all our experiments.

\section{Pascal VOC}
The Pascal VOC competition has

\section{New York University RGB-D Segmentation

### 2013-09-08 intro.tex
remove all occurences of i.e. and e.g. minor fixes
FIX put chapter commands in separate files, so that the text is not on a new page...
removed dataset blabla, maybe in appendix. added contained papers to the intro.

\section{Overview}
What does this theses contribute?

Why semantic segmentation?
Why is it not solved yet?

@@

>>>>

\chapter{Introduction}

@@

Why semantic segmentation? Difference object / stuff centric? -> difference to Alex
Why is it not solved yet?

Structured approaches, latent variable approaches

\section{List of Contributions}
Contributions:
- Introduces general clustering algorithm that improves pipeline in serveral places
- Shows that weakly supervised object class segmentation (not semantic segmentation) is possible
- Provides general efficient framework for structured prediction
- Analyze max-margin learning algorithms in different regimes
- shows exact learning is possible in loopy graphs and improves results (sometimes?)
- shows importance of edge features
- Demonstrates how latent variables benefit semantic segmentation

\section{Publications}
The main material of this thesis has either been published in conference proceedings or has been
submitted to conferences or journals. We now list the relevant publications.
\begin{description}
    \item[Chapter 2] \emph{Information Theoretic Clustering using Minimum Spanning Trees} Andreas C. M\"uller, Sebastian Nowozin and Christoph H. Lampert. Published in the proceedings of the German Conference on Pattern Recognition.
    \item[Chapter 3] \emph{Multi-Instance Methods for Partially Supervised Image Segmentation} Andreas C. M\"uller and Sven Behnke. Published in the proceedings of the IARP Worshop on Partially Supervised Learning.
    \item[Chapter 4] \emph{PyStruct - Structured Prediction in Python} Andreas C. M\"uller and Sven Behnke. Submitted to the Journal of Machine Learning Research, Open Source Software track.
    \item[Chapter 5] \emph{Learning a Loopy Model for Semantic Segmentation Exactly}. Andreas C. M\"uller and Sven Behnke. Submitted to the International Conference on Computer Vision Theory and Applications.
    \item[Chapter 6] \emph{Learning Depth-Sensitive Conditional Random Fields for Semantic Segmentation}. Andreas C. M\"uller and Sven Behnke. Submitted to the International Conference on Robotics and Automation.
\end{description}
